Adaptive Approximation for Multivariate Linear Problems with Inputs Lying in a Cone

### 2020-01-25 DingHickKritzMakRICAMChapVerF.tex

Figures \ref{fig:four} (a) and (b) display the total required sample size from Algorithm \ref{DHKM:InfPilotConeAlg}, as a function of the error to tolerance ratio, $\|f - \DHKMALG(f,\varepsilon)\|_\infty/\varepsilon$, in $d=4$ and $d=7$ dimensions, respectively. Each data point corresponds to a different error tolerance $\varepsilon$. A ratio $\|f - \DHKMALG(f,\varepsilon)\|_\infty/\varepsilon$ close to, but not exceeding, one is desired, since this shows that our adaptive algorithm is successful. For $d=4$, $\|f - \DHKMALG(f,\varepsilon)\|_\infty/\varepsilon$ fluctuates around 0.4 for all choices of $\varepsilon$; for $d=7$, this ratio begins at $\approx 0.1$ for $\varepsilon = 0.1$, then decreases to $\approx 0.014$ for $\varepsilon = 0.001$. This shows that our adaptive approximation algorithm works reasonably well.  It appears slightly more effective in lower dimensions  than in higher dimensions. A likely reason is that the underlying POSD structure can be more easily learned from a small pilot sample in lower dimensions than in higher dimensions.

>>>>

Figures \ref{fig:four} (a) and (b) display the total required sample size from Algorithm \ref{DHKM:InfPilotConeAlg}, as a function of the error to tolerance ratio, $\|f - \DHKMALG(f,\varepsilon)\|_\infty/\varepsilon$, in $d=4$ and $d=7$ dimensions, respectively. Each data point corresponds to a different error tolerance $\varepsilon$. A ratio $\|f - \DHKMALG(f,\varepsilon)\|_\infty/\varepsilon$ close to, but not exceeding, one is desired, since this shows that our adaptive algorithm is successful. For $d=4$, $\|f - \DHKMALG(f,\varepsilon)\|_\infty/\varepsilon$ fluctuates around 0.3 for all choices of $\varepsilon$; for $d=7$, this ratio begins at $\approx 0.1$ for $\varepsilon = 0.1$, then decreases to $\approx 0.01$ for $\varepsilon = 0.001$. This shows that our adaptive approximation algorithm works reasonably well.  It appears slightly more effective in lower dimensions  than in higher dimensions. A likely reason is that the underlying POSD structure can be more easily learned from a small pilot sample in lower dimensions than in higher dimensions.
